Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-08 Tex/CAV2019/replyVSTTEJUNE2020.tex
VSTTE rebuttal

\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{url}
%\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[nodayofweek]{datetime}
\usepackage[caption=false]{subfig}
%\mathtoolsset{showonlyrefs}
\usepackage[linesnumbered,lined,ruled,boxed]{algorithm2e}
\SetKw{KwBy}{by}
\usepackage{xcolor}
%\input{rgbcolors}
%\usepackage{color}
\usepackage{natbib}
% \usepackage[style=authoryear-comp,dashed=false]{biblatex}
% \bibliography{piecewise_lyapunov}
\newtheorem{myassumption}{Assumption}
\newcommand{\mstitle}{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison}
\newcommand{\refnumber}{Paper 14}
\newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
\newcommand{\comment}[1]{}
%\definecolor{DarkGreen}{rgb}{0.2, 0.4, 0.2}
\usepackage{amsmath}
\usepackage{listings}
\lstset{language=C,basicstyle=\small\ttfamily}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, calc,patterns,decorations.pathmorphing,decorations.markings}

@@

According to the reviewers' comments, our manuscript was carefully revised, and all detailed changes are highlighted in blue color, along with the original text. The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections.

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. We had to revise the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile. Our manuscript was entirely revised, and the PV sizing modeling was changed to a higher level of explanation, with a flowchart. The proposed synthesis algorithm followed the same principle. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF file that can be accessed.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again. Indeed, we had to revise the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing. We must realize as well, and we added a highlight about this in the Results section. An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same. 
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. You are correct; Reviewer \#1 also provided the same observation. We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed.
\end{resposta}

@@

\begin{resposta}
We agree with the reviewer. We missed the details about why those values are taken. Therefore, we revised the corresponding online text to: ``The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime''.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. Those are the same observations did by Reviewer \#1 and \#2. We had to revise the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4). In Section 3, the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}

>>>>

\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
%\usepackage{url}
\usepackage{hyperref}
%\usepackage{mathtools}
\usepackage{enumerate}
\usepackage[nodayofweek]{datetime}
\usepackage[caption=false]{subfig}
%\mathtoolsset{showonlyrefs}
\usepackage[linesnumbered,lined,ruled,boxed]{algorithm2e}
\SetKw{KwBy}{by}
\usepackage{xcolor}
%\input{rgbcolors}
%\usepackage{color}
\usepackage{natbib}
% \usepackage[style=authoryear-comp,dashed=false]{biblatex}
% \bibliography{piecewise_lyapunov}
\newtheorem{myassumption}{Assumption}
\newcommand{\mstitle}{Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison}
\newcommand{\refnumber}{Paper 14}
\newenvironment{resposta}{~~~\begin{quote}\color{blue}\textbf{Response:}}{\end{quote}}
\newcommand{\comment}[1]{}
%\definecolor{DarkGreen}{rgb}{0.2, 0.4, 0.2}
\usepackage{amsmath}
\usepackage{listings}
\lstset{language=C,basicstyle=\small\ttfamily}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, calc,patterns,decorations.pathmorphing,decorations.markings}

@@

According to the reviewers' comments, our manuscript was carefully revised%, and all detailed changes are highlighted in blue color, along with the original text
. The revision included the Abstract, Introduction, Background, Synthesizing Optimal Sizing, Results, and Conclusions sections. A highlighted version of the entire paper is available in \url{https://tinyurl.com/y9scqv6g} if the reviewers would like access.

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. We had to revise parts of the Background and the Synthesizing Optimal Sizing sections to address the right conference attendants' profile. The PV sizing modeling was changed to a higher level of explanation, with a flowchart in page 6 (Fig.4). The proposed synthesis algorithm followed the same principle in page 8. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that we removed from the paper, we created a link to a 5-page PDF online file that can be accessed.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer again. Indeed, we had to revise parts of the Abstract, the Introduction, and the Synthesizing Optimal Sizing sections in order to address more correctly what is PV optimal sizing. We must realize as well, and we added a highlight about this in the Results section: "An optimal solution from a tool is not necessarily the same optimal of another tool, mainly when the database of equipment items (with different costs) are not the same." 
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for this insightful comment and suggestion. You are correct; Reviewer \#1 also provided the same observation. We had to revise parts of the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4 at page 6). In Section 3 (page 8), the synthesis algorithm followed the same idea. Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that was removed from this revised paper, we created a link to a 5-page PDF complementary file that can be accessed.
\end{resposta}

@@

\begin{resposta}
We agree with the reviewer. We missed the details about why those values are taken. Considering that the new paper version has a higher level explanation for the PV sizing, we removed this part and transferred it to the complementary PDF text. Therefore, we revised the corresponding online text to: ``The $DOD$ is usually $25$\% for lead-acid batteries, and $80$\% for lithium batteries and represent an intrinsic and empirical feature of those type of batteries [Pinho and Galdino, 2014] in order to guarantee its lifetime''.
\end{resposta}

@@

\begin{resposta} 
We thank the reviewer for these insightful comments and suggestions. Those are the same observations did by Reviewer \#1 and \#2. We had to revise parts of the Background, and the Synthesizing Optimal Sizing sections to address the right conference attendants profile. Our manuscript was revised, and the PV sizing modeling was changed to a higher level of explanation, including a flowchart in Section 2 (cf. Figure 4 at page 6). In Section 3, the synthesis algorithm followed the same idea (page 8). Besides that, in case of interest in the complete and detailed mathematical sizing of PV systems, that was removed from this revised version of the paper, we created a link to a 5-page PDF complementary file that can be accessed as well.
\end{resposta}
